Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-17 paper/manuscript.tex
legend for Figure 6

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/FI6v3mutant_neutcurves/FI6v3_mutant_neutcurves.pdf}}
\caption{
\label{fig:FI6v3neutcurves}
\comment{The neutralization curves look good, except can you make the different mutations have different shapes as well as different colors.
Also, I think it would be good to show the P80D and V135T neutralization curves versus H17-L7 and H17-L19, respectively.
So your current figure could be panel (A), and then these could be below and be called panel (B) and (C). Each panel could also be labeled with the antibody name.
You can get these neutralization curves from Mike's paper. 
I think the data for them is in his paper repository, but if you can't find it then perhaps e-mail him to ask if he knows, or I can help look for it too.
The rationale here is that it will provide an illustration of the difference between the ``large effect'' mutations for other antibodies and the ``small effect'' ones for these FI6v3. 
}
}
\end{figure}

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.8\textwidth]{figs/FI6v3mutant_neutcurves/FI6v3_mutant_neutcurves.pdf}}
\caption{
\label{fig:FI6v3neutcurves}
{\bf The mutations selected by FI6v3 increase neutralization resistance, but the effects are small.}
(A) Neutralization curves of individual viral mutants with FI6v3.
The mutations K280S, K280T, N291S, G47R (HA2), and K(-8)T are all expected to increase neutralization resistance based on the mutational antigenic profiling (Figure~\ref{fig:structures}A), and they all do so -- but only modestly. 
The mutations K280A, M17L (HA2), P80D, and V135T are \emph{not} expected to affect neutralization based on the mutational antigenic profiling (Figure~\ref{suppfig:FI6v3logo}, and none of them do.
(B), (C) In contrast to FI6v3, mutations selected by other antibodies have very large effects on neutralization.
Shown are neutralization curves for representative escape mutants from H17-L19 and H17-L2 taken from \citet{doud2017complete}; that paper also shows additional examples of large-effect escape mutations from these antibodies.
}
\end{figure}
